---
title: "Data Scientist's Toolbox"
author: "slowLearner"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Course Project

### Purpose

To demonstrate that I have the basic toolbox properly installed and working on my machine.
This document itself also demonstrates the use of the installed rmarkdown package.

### Details
##### R is installed:  
```{r}
sessionInfo()
```
##### Git is installed:
```{r}
x <- system('git --version', intern=TRUE)
print(x)
```
##### RStudio is installed.

I wanted to use inline command `RStudio.Version()` here but it does not work because when you `knit` a .Rmd file, it happens in a separate R session outside of RStudio.

> <font size=2>*"This is as intended; documents are knitted in a clean, separate R session outside of the main RStudio session. If you need to knit in your main R session"* See <https://github.com/rstudio/rstudio/issues/6892></font>

4. I have a GitHub account (obviously ;-).

---